GWAS_Prep

### 2019-09-30 Analysis/01_GWAS_Prep.Rmd
Rename files

```{r}
# Read in data and packages
# install.packages("Biocmanager")
library(gwascat) # BiocManager::install("gwascat")
library(dplyr)   # install.packages("dplyr")
source("https://raw.githubusercontent.com/mdozmorov/MDmisc/master/R/unembed.R") # library(MDmisc)  
# install.packages("rJava")
library(rowr)    # install.packages("rowr")
library(readr)   # install.packages("readr")
```

@@

  #Summarise the results
  #Keeping track of changes (sapply necessary to keep placeholders for unmapped genes)
  recomb_genes = sapply(ebi_dat$MAPPED_GENE, function(x) alias2SymbolEbicat(x, species = "Hs"))
  recomb_genes = unlist(lapply(recomb_genes, function(x) paste0(x,collapse=' ')))
  change = (ebi_dat$MAPPED_GENE == recomb_genes)
  sum_vec = ifelse(change == TRUE, "Same", ifelse(change == FALSE & recomb_genes == "", "No Match", "Converted"))
  ebi_dat$MAPPED_GENE = recomb_genes
  return(ebi_dat)
}

>>>>

```{r}
# Read in data and packages
# install.packages("Biocmanager")
library(gwascat) # BiocManager::install("gwascat")
library(limma) # BiocManager::install("limma")
library(dplyr)   # install.packages("dplyr")
source("https://raw.githubusercontent.com/mdozmorov/MDmisc/master/R/unembed.R") # library(MDmisc)  
# install.packages("rJava")
library(rowr)    # install.packages("rowr")
library(readr)   # install.packages("readr")

@@

  #Summarise the results
  #Keeping track of changes (sapply necessary to keep placeholders for unmapped genes)
  recomb_genes = sapply(ebi_dat$MAPPED_GENE, function(x) alias2Symbol(x, species = "Hs"))
  recomb_genes = unlist(lapply(recomb_genes, function(x) paste0(x,collapse=' ')))
  change = (ebi_dat$MAPPED_GENE == recomb_genes)
  sum_vec = ifelse(change == TRUE, "Same", ifelse(change == FALSE & recomb_genes == "", "No Match", "Converted"))
  ebi_dat$MAPPED_GENE = recomb_genes
  return(ebi_dat)
}
